---
title: "Healthcare quality"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr) 
library(ggplot2)
library(plotly)

h <- read.csv("hospitals.csv")

# correct order of levels
h <- h %>%group_by(state) %>% 
  mutate(n = n())

for (i in 5:11) {  
  h[[i]] <- factor(h[[i]], levels(h[[i]])[c(3,4,2,1)])
}
h$Overall_rating <- factor(h$Overall_rating, levels(h$Overall_rating)[c(6, 1:5)]) 
# End of correct order of levels

#################################
graph <- function(data, tab = h){  # helper plotting graphs
  if (data == "Overall_rating") {
    ggplot(tab, aes(x=reorder(state,-n))) +
      geom_bar(aes(fill=`Overall_rating`)) +   # Overall rating
      scale_fill_manual("Score", values = c("lightgray", "#d7191c","#fdae61", "#ffffbf", "#a6d96a", "#1a9641")) + #colors - http://colorbrewer2.org/#type=diverging&scheme=RdYlGn&n=5
      geom_vline(aes(xintercept = which(levels(reorder(state, -n)) %in% "AL")), color = "grey") +
      theme_minimal() + labs( x = "State", y = "Number of hospitals") +
      theme(legend.position = c(0.8, 0.7))
  } else if (data == "Type") {
    ggplot(tab, aes(x=reorder(state,-n))) +
      geom_bar(aes(fill=Type)) +   # Type
      geom_vline(aes(xintercept = which(levels(reorder(state, -n)) %in% "AL")), color = "grey") +
      theme_minimal() + labs( x = "State", y = "Number of hospitals")
  } else {
    ggplot(tab, aes(x=reorder(state,-n))) +
      geom_bar(aes_string(fill=data)) +   
      scale_fill_manual("Score", values = c("lightgray","orange","red", "green")) +
      geom_vline(aes(xintercept = which(levels(reorder(state, -n)) %in% "AL"))) +
      theme_minimal() + labs( x = "State", y = "Number of hospitals") +
      theme(legend.position = c(0.7, 0.7))
  }

}
####################  end of graph function

hospitals <- read.csv("hospitals_perc.csv")

#####################
graph_perc <- function(cat, h = hospitals) {
  hospitals <- h
  tmp <- filter(hospitals, category == cat)
  tmp <- droplevels(tmp)
  
  if (cat =="Overall_rating") {
    tmp$Values <- factor(tmp$Values, levels(tmp$Values)[c(6, 1:5)])  #correct order of levels
  #  tmp[tmp$Values=="1",2] <- tmp[tmp$Values=="1",2] *-1
    tmp <- tmp %>% group_by(state) %>% 
      mutate(above = if_else(Values == "5", Freq, 0)) %>% 
      arrange(state)
    
    ggplot(tmp, aes(x=reorder(state, -above), y = Freq*100)) +
      geom_col(aes(fill = Values)) +
      scale_fill_manual("Score", values = c("lightgray", "#d7191c","#fdae61", "#ffffbf", "#a6d96a", "#1a9641")) + #colors - http://colorbrewer2.org/#type=diverging&scheme=RdYlGn&n=5
      geom_vline(aes(xintercept = which(levels(reorder(state, -above)) %in% "AL"))) +
      theme_minimal()+ labs( x = "State", y = "% of hospitals")
    
  } else if (cat == "Type") {
    ggplot(tmp, aes(x=state, y = Freq*100)) +
      geom_col(aes(fill = Values)) +
     # scale_fill_manual("") +
      geom_vline(aes(xintercept = state %in% "AL"), color = "grey") +
      theme_minimal()+ labs( x = "State", y = "% of hospitals")
    
  } else {
    tmp$Values <- factor(tmp$Values, levels(tmp$Values)[c(3, 2, 4, 1)])  #correct order of levels
    tmp[tmp$Values=="Below the national average",2] <- tmp[tmp$Values=="Below the national average",2] *-1
    tmp <- tmp %>% group_by(state) %>% 
      mutate(above = if_else(Values == "Above the national average", Freq, 0)) %>% 
      arrange(state)
    
    ggplot(tmp, aes(x=reorder(state, -above), y = Freq*100)) +
      geom_col(aes(fill = Values)) +
      scale_fill_manual("Score", values = c("lightgray", "red", "orange", "green")) +
      geom_vline(aes(xintercept = which(levels(reorder(state, -above)) %in% "AL"))) +
      theme_minimal()+ labs( x = "State", y = "% of hospitals")
  }
}
########################## end of graph_perc function

######################### Ranking function
ranking <- function(cat, data = hospitals) {
     h <- data
     ranking <- filter(h, category == cat & Values != "Not Available")
     ranking[ranking$Values=="Below the national average",2] <- ranking[ranking$Values=="Below the national average",2] *-1
     tmp <- filter(ranking, Values == "Same as the national average")
     tmp$Freq <- 0
     tmp1 <- filter(ranking, Values != "Same as the national average")
     tmp1 <- tmp1 %>% group_by(state) %>% mutate(Freq = sum(Freq)) #pozytywne wartosci netto
     
     ranking <- bind_rows(tmp, tmp1) %>% filter(Values != "Below the national average") %>% 
          mutate(above = if_else(Values == "Above the national average", Freq, 0))
     ranking$Freq <- ranking$Freq*100
     
     # ggplot(ranking, aes(x=reorder(state, -above), y = Freq)) +
     #      geom_col(aes(fill = Values)) +
     #      geom_vline(aes(xintercept = which(levels(reorder(state, -above)) %in% "AL")))

     x <- filter(ranking, Values == "Above the national average") %>% arrange( desc(Freq))
     third <- x[3,c("state","Freq")]  #third place
     al <- x[x$state == "AL",c("state","Freq")] #Alaska result
     al <- filter (al, Freq == min(Freq))
    # al <- al[1,]
     
     rank <- cbind (t(third), t(al))
     colnames(rank) <- c("Third", "Alaska")
     rownames(rank) <- c("State", as.character(ranking$category)[1])
     rank
}
########################## End of ranking function
 
```




Hospitals
=====================================  



Row {.tabset .tabset-fade}
-------------------------------------

### Overall Rating in %

```{r, fig.width=12}
graph_perc("Overall_rating")
```

### Overall Rating

```{r, fig.width=12}
graph("Overall_rating") #%>% ggplotly() %>% layout(hovermode = 'compare')
```


Row {.tabset .tabset-fade}
-------------------------------------

### Mortality in %
```{r, fig.width=12}
graph_perc("Mortality")
```

### Mortality
```{r, fig.width=12}
graph("Mortality")
```



Row  {.tabset .tabset-fade}
-------------------------------------

### Safety of Care in %

```{r, fig.width=12}
graph_perc("Safety_of_care")
```


### Safety of Care

```{r, fig.width=12}
graph("Safety_of_care")
```

Row  {.tabset .tabset-fade}
-------------------------------------

### Readmission in %

```{r, fig.width=12}
graph_perc("Readmission")
```

### Readmission

```{r, fig.width=12}
graph("Readmission")
```

Row  {.tabset .tabset-fade}
-------------------------------------

### Patient experience in %

```{r, fig.width=12}
graph_perc("Patient_experience")
```

### Patient experience

```{r, fig.width=12}
graph("Patient_experience")
```

Row  {.tabset .tabset-fade}
-------------------------------------

### Effectiveness of Care in %

```{r, fig.width=12}
graph_perc("Effectiveness_of_Care")
```

### Effectiveness of Care in %

```{r, fig.width=12}
graph("Effectiveness_of_Care")
```


Row  {.tabset .tabset-fade}
-------------------------------------

### Timeliness of Care in %

```{r, fig.width=12}
graph_perc("Timeliness_of_Care")
```

### Timeliness of Care

```{r, fig.width=12}
graph("Timeliness_of_Care")
```

Row  {.tabset .tabset-fade}
-------------------------------------

### Efficient use of medical imaging in %

```{r, fig.width=12}
graph_perc("Medical_imaging")
```

### Efficient use of medical imaging 

```{r, fig.width=12}
graph("Medical_imaging")
```


Physicians
=====================================  

```{r}
ph1 <- read.csv("physician.csv")
graph_ph <- function (title, data = ph1) {
     ph1 <- data
     tmp <- filter(ph1, measure_title == title) %>% 
          group_by(state) %>% 
          summarise(performance = mean(measure_performance_rate, na.rm = TRUE)) %>% 
          droplevels(.)
     
     tmp$performance <- coalesce(tmp$performance, 0) #remove of NAs
     
     third <- levels(reorder(tmp$state, -tmp$performance))[3]
     third <- filter(tmp, state == third)
     
     ggplot(tmp, aes(x=reorder(state, -performance), y = performance)) +
          geom_col(aes(fill = ifelse(state == "AL",1,0))) +
          geom_hline(aes(yintercept = third$performance), color = "grey") +
     #     geom_segment(x = 18, y = 28, xend = 18, yend = third$performance, col = "red") +
          geom_text(data = filter(tmp, state == "AL"), aes(label = performance), vjust = 1.5) +
          geom_text(data = filter(tmp, state == "AL"), aes(label = round(third$performance, digits = 0)), y = third$performance+1.5) +     
          theme_minimal() + labs( x = "State", y = "Measure of performance") +
          guides(fill=FALSE)
}
```

Row 
-------------------------------------

### Attention to patient medicine cost

```{r, fig.width=12}
graph_ph("Attention to patient medicine cost." )
```

Row 
-------------------------------------

### Between visit communication

```{r, fig.width=12}
graph_ph("Between visit communication." )
```

Row 
-------------------------------------

### Clinicians working together for your care

```{r, fig.width=12}
graph_ph("Clinicians working together for your care." )
```

Row 
-------------------------------------

### Courteous and helpful office staff

```{r, fig.width=12}
graph_ph("Courteous and helpful office staff." )
```

Row 
-------------------------------------

### Getting timely care, appointments, and information

```{r, fig.width=12}
graph_ph("Getting timely care, appointments, and information." )
```

Row 
-------------------------------------

### Health promotion and education

```{r, fig.width=12}
graph_ph("Health promotion and education." )
```

Row 
-------------------------------------

### How well clinicians communicate

```{r, fig.width=12}
graph_ph("How well clinicians communicate." )
```

Row 
-------------------------------------

### Patients' rating of clinicians

```{r, fig.width=12}
graph_ph("Patients' rating of clinicians." )
```